---
title: "OpenHDF5"
author: "Kunxuan Wang"
date: "June 20, 2016"
output: html_document
---


```{r load-libraries }
library(raster)
library(rgdal)
library(rhdf5)

```

##open a file
use tab for auto complete filepaths 
```{r select-file }
# set file name
f <- "../NEONdata/D17-California/TEAK/2013/spectrometer/reflectance/Subset3NIS1_20130614_100459_atmcor.h5"

# view h5 structure
h5ls(f)
```

different h5 files can have different format
```{r import-spatial-info}
# import spatial infomation
mapInfo <- h5read(f,
                  "map info", 
                  read.attributes = TRUE)
mapInfo
```

str(scaleFactor) - view structure of obj
```{r get-reflectance-metadata}
# read in refl data attributes
reflInfo <-h5readAttributes(f,
                            "Reflectance") #read only attributes
#(file = f, name = "Reflectance") - full code
reflInfo

# define atributes
scaleFactor <- reflInfo$`Scale Factor`
noDataValue <- as.numeric(reflInfo$`data ignore value`)

```

look at how big the data is 
R is column major: col x row x band
R starts indexing at 1
```{r import-dims}
# import data dimensions
fid <- H5Fopen(f) #connection to h5 file, can over write file
did <- H5Dopen(fid, "Reflectance")

# get data set dimensions
sid <- H5Dget_space(did) # structure of dataset
dims <- H5Sget_simple_extent_dims(sid)$size

# close all open connections
H5Sclose(sid)
H5Dclose(did)
H5Fclose(fid)

```

read in reflectance data
```{r read-data}
# extract slice of data file
b56 <- h5read(f,
              "Reflectance",
              index=list(1:dims[1], 1:dims[2], 56))
b56

class(b56)


```

convert data to matrix
```{r convert-matrix}
b56 <- b56[,,1]
class(b56)

```

plot
```{r plot-data}
image(b56)
image(log(b56),main="log transformed data") #apply image stretch 

hist(b56)

```

##Data Clean up
```{r data-clean-up}
# remove no data value
b56[b56 == noDataValue] <- NA

# apply scale factor
b56 <- b56 / scaleFactor

hist(b56)

```


## Transpose Data
```{r transpose-data}
b56 <- t(b56)
image(b56)

```

## Create Spatial Extent
```{r create-spatial-extent}
# split mapInfo obj
mapInfo <- unlist(strsplit(mapInfo, ","))

# define upper left had corner coordinate
xMin <- as.numeric(mapInfo[4])
yMax <- as.numeric(mapInfo[5])

# get spatial resolution
xRes <- as.numeric(mapInfo[6])
yRes <- as.numeric(mapInfo[7])

# Calculate xMax & yMin
xMax <- xMin + (xRes * dims[1])
yMin <- yMax - (yRes * dims[2]) 

```

## Create Spatial Extent
```{r creat-extent}
rasExt <- extent(xMin, xMax, yMin, yMax)
rasExt

```

crs - coordinate ref system
## Create Raster Object
```{r create-raster}
b56r <- raster(b56, 
               crs=CRS("+init=epsg:32611"))  
extent(b56r) <- rasExt
b56r
plot(b56r, main = "spatial ref data")

```

# Import NEON Functions
```{r import-using-functions}
# install.packages("devtools")
library(devtools)

# install_github("lwasser/neon-aop-package/neonAOP")
library(neonAOP)

b55 <- open_band(f, 
                 bandNum = 55,
                 epsg = 32611)
plot(b55)


epsg <- 32611
# import several bands
#bands <- c(58, 34, 19)
bands <- c(90, 34, 19)

# creat raster stack
RGBStack <- create_stack(f, 
                         bands = bands,
                         epsg = epsg)
#plot(RGBStack)
plotRGB(RGBStack, stretch='lin')

```
more information on functions 
http://neon-workwithdata.github.io/neon-data-institute-2016/R/open-NEON-hdf5-functions/

added change
